Supporting information - Bayesian regression facilitates quantitative modelling of cell metabolism

### 2024-02-12 paper/main.qmd
Final resubmission changes

---
title: "Bayesian regression facilitates quantitative modelling of cell metabolism"
keywords: Bayesian inference, kinetic models of cell metabolism, 
          multiomics integration, ordinary differential equations,
          regulatory anlaysis
abstract: >
  This paper presents Maud, a command-line application that implements Bayesian
  statistical inference for kinetic models of biochemical metabolic reaction
  networks. Maud takes into account quantitative information from omics
  experiments and background knowledge, as well as structural information about
  kinetic mechanisms, regulatory interactions and enzyme knockouts. Our paper
  reviews the existing options in this area, presents a case study illustrating
  how Maud can be used to analyse a metabolic network and explains the
  biological, statistical and computational design decisions underpinning Maud.
number-sections: true
author: 
  - name: "Teddy Groves"
    orcid: 0000-0002-7109-3270
    email: tedgro@biosustain.dtu.dk
    affiliations: 
      - id: biosustain
        name: DTU
        department: The Novo Nordisk Foundation Center for Biosustainability
        city: Kongens Lyngby 2800
        country: Denmark
    attributes:
      corresponding: true
      equal-contributor: true
    note: These authors contributed equally to this research.
  - name: "Nicholas Luke Cowie"
    orcid: 0000-0003-3367-2105
    affiliations: 
      - ref: biosustain
    attributes:
      equal-contributor: true
    note: These authors contributed equally to this research.
  - name: "Lars Keld Nielsen"
    orcid: 0000-0001-8191-3511
    affiliations: 
      - id: uq
        name: The University of Queensland
        department: Australian Institute for Bioengineering and Nanotechnology (AIBN)
        city: St Lucia 4067
        country: Australia
      - ref: biosustain
bibliography: bibliography.bib
format:
  acs-pdf:
    keep-tex: true
    journal:
      id: asbcd6  #This is an identifier for the target journal: from https://pubs.acs.org/, the identifier is the part of the URL after https://pubs.acs.org/journal/, e.g. for J. Org. Chem. it would be joceah.
      type: article  #article, note, communication, review, letter, or perspectivee
      layout: traditional #traditional or twocolumn, twocolumn currently broken for longtables
      hide-email: false # if enabled, hides email addresses (and fax/phone)
  acs-html:
   include-in-header: mathjax.html
   embed-resources: true
  docx: default
---

@@

<!--:::{.callout-important title="Changes"}-->
Maud uses Markov Chain Monte Carlo to perform posterior inference on a Bayesian
statistical model. This section introduces these topics and then describes
exactly what kind of Bayesian statistical model Maud uses.

@@

Maud employs adaptive Hamiltonian Monte Carlo to perform posterior inference
for a Bayesian statistical model where the process model is the kinetic model
described above. The next two subsections describe Maud's prior and measurement
models.
<!--:::-->

>>>>

---
affiliations:
  - id: biosustain
    name: "DTU"
    department: "The Novo Nordisk Foundation Center for Biosustainability"
    city: "Kongens Lyngby 2800"
    country: "Denmark"
  - id: uq
    name: "The University of Queensland"
    department: "Australian Institute for Bioengineering and Nanotechnology (AIBN)"
    city: "St Lucia 4067"
    country: "Australia"
author: 
  - name: "Teddy Groves"
    orcid: "0000-0002-7109-3270"
    email: "tedgro@biosustain.dtu.dk"
    affiliations:
      - ref: biosustain
  - name: "Nicholas Luke Cowie"
    affiliations:
      - ref: biosustain
    orcid: "0000-0003-3367-2105"
  - name: "Lars Keld Nielsen"
    affiliations:
      - ref: uq
      - ref: biosustain
    orcid: "0000-0001-8191-3511"
title: "Bayesian regression facilitates quantitative modelling of cell metabolism"
keywords: Bayesian inference, kinetic models of cell metabolism, 
          multiomics integration, ordinary differential equations,
          regulatory anlaysis
abstract: >
  This paper presents Maud, a command-line application that implements Bayesian
  statistical inference for kinetic models of biochemical metabolic reaction
  networks. Maud takes into account quantitative information from omics
  experiments and background knowledge, as well as structural information about
  kinetic mechanisms, regulatory interactions and enzyme knockouts. Our paper
  reviews the existing options in this area, presents a case study illustrating
  how Maud can be used to analyse a metabolic network and explains the
  biological, statistical and computational design decisions underpinning Maud.
number-sections: true
bibliography: bibliography.bib
format:
  acs-pdf:
    keep-tex: true
    journal:
      id: asbcd6  #This is an identifier for the target journal: from https://pubs.acs.org/, the identifier is the part of the URL after https://pubs.acs.org/journal/, e.g. for J. Org. Chem. it would be joceah.
      type: article  #article, note, communication, review, letter, or perspectivee
      layout: traditional #traditional or twocolumn, twocolumn currently broken for longtables
      hide-email: false # if enabled, hides email addresses (and fax/phone)
  acs-html:
   include-in-header: mathjax.html
   embed-resources: true
  docx: default
---

@@

<!-- :::{.callout-important title="Changes"} -->
Maud uses Markov Chain Monte Carlo to perform posterior inference on a Bayesian
statistical model. This section introduces these topics and then describes
exactly what kind of Bayesian statistical model Maud uses.

@@

Maud employs adaptive Hamiltonian Monte Carlo to perform posterior inference
for a Bayesian statistical model where the process model is the kinetic model
described above. The next two subsections describe Maud's prior and measurement
models.
<!-- ::: -->

### 2024-02-12 paper/supporting_information.qmd
Final resubmission changes

---
title: Supporting information - Bayesian regression facilitates quantitative modelling of cell metabolism
format:
  html:
    embed-resources: true
    include-in-header: mathjax.html
  acs-pdf: 
    include-in-header: 
      - text: \renewcommand{\thepage}{S\arabic{page}}
    keep-tex: true
    journal:
      id: asbcd6  #This is an identifier for the target journal: from https://pubs.acs.org/, the identifier is the part of the URL after https://pubs.acs.org/journal/, e.g. for J. Org. Chem. it would be joceah.
      type: article  #article, note, communication, review, letter, or perspectivee
      layout: traditional #traditional or twocolumn, twocolumn currently broken for longtables
  docx: default
number-sections: true
author: 
  - name: "Teddy Groves"
    orcid: 0000-0002-7109-3270
    email: tedgro@biosustain.dtu.dk
    affiliations: 
      - id: biosustain
        name: DTU
        department: The Novo Nordisk Foundation Center for Biosustainability
        city: Kongens Lyngby 2800
        country: Denmark
    attributes:
      corresponding: true
      equal-contributor: true
    note: These authors contributed equally to this research.
  - name: "Nicholas Luke Cowie"
    orcid: 0000-0003-3367-2105
    affiliations: 
      - ref: biosustain
    attributes:
      equal-contributor: true
    note: These authors contributed equally to this research.
  - name: "Lars Keld Nielsen"
    orcid: 0000-0001-8191-3511
    affiliations: 
      - id: uq
        name: The University of Queensland
        department: Australian Institute for Bioengineering and Nanotechnology (AIBN)
        city: St Lucia 4067
        country: Australia
      - ref: biosustain
bibliography: bibliography.bib
---

>>>>

---
affiliations:
  - id: biosustain
    name: "DTU"
    department: "The Novo Nordisk Foundation Center for Biosustainability"
    city: "Kongens Lyngby 2800"
    country: "Denmark"
  - id: uq
    name: "The University of Queensland"
    department: "Australian Institute for Bioengineering and Nanotechnology (AIBN)"
    city: "St Lucia 4067"
    country: "Australia"
author: 
  - name: "Teddy Groves"
    orcid: "0000-0002-7109-3270"
    email: "tedgro@biosustain.dtu.dk"
    affiliations:
      - ref: biosustain
  - name: "Nicholas Luke Cowie"
    affiliations:
      - ref: biosustain
    orcid: "0000-0003-3367-2105"
  - name: "Lars Keld Nielsen"
    affiliations:
      - ref: uq
      - ref: biosustain
    orcid: "0000-0001-8191-3511"
title: Supporting information - Bayesian regression facilitates quantitative modelling of cell metabolism
format:
  html:
    embed-resources: true
    include-in-header: mathjax.html
  acs-pdf: 
    include-in-header: 
      - text: \renewcommand{\thepage}{S\arabic{page}}
    keep-tex: true
    journal:
      id: asbcd6  #This is an identifier for the target journal: from https://pubs.acs.org/, the identifier is the part of the URL after https://pubs.acs.org/journal/, e.g. for J. Org. Chem. it would be joceah.
      type: article  #article, note, communication, review, letter, or perspectivee
      layout: traditional #traditional or twocolumn, twocolumn currently broken for longtables
  docx: default
number-sections: true
bibliography: bibliography.bib
---
